---
title: "Assignment 4"
author: "Garrett Matthews"
date: "February 5, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
df = read.csv("landdata-states.csv", colClasses = c("State"="character"))


```

## Questions:
  + 1: **read.csv also automatically assigns the values in the first row as the names for the columns, reads       . as decimal values, and will add rows to make all columns of equal length**
  + 2: **read.csv2() is deliminated by semicolons**
  + 3: **Because in Europe commas are used as the decimal marker** 
  
  + 4: **You could change the class of state by using the colClasses function: 'colClasses = **
       ** c("State"="character")'**
       
  + 5: ** summary(df$Home.Value) gives the summary for only Home.Value**
  + 6: ** The name of the fourth column, Home.Value is returned**
  
  

```{r, echo=TRUE}
hist(df$Land.Value) # histogram showing number of times each numeric value was seen in the vector "Land.Value"

# If you want to look at land value by region, you could do this:
plot(x=df$region,y=df$Land.Value)

# Land value by year
plot(x=df$Year,y=df$Land.Value,col=df$region)
```

  + 7: **It colors the points according to their value in the region column**

